---
title: "Milestone"
author: "Sandra Müller"
date: "10 2 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(stringr, quietly = TRUE, warn.conflicts = FALSE)
library(quanteda, quietly = TRUE, warn.conflicts = FALSE)
library(textmineR, quietly = TRUE, warn.conflicts = FALSE)
```
    
## Task

```{r}

twitter <- readLines("final/en_US/en_US.twitter.txt", skipNul = TRUE, warn = FALSE)
blogs <- readLines("final/en_US/en_US.blogs.txt", skipNul = TRUE, warn = FALSE)
news <- readLines("final/en_US/en_US.news.txt", skipNul = TRUE, warn = FALSE)
allfiles <- unlist(list(twitter, blogs, news))
```

## Basic data for files

```{r}
print(length(twitter))
print(length(blogs))
print(length(news))


```

## Basic clean ups

```{r}

allfilesSample <- sample(allfiles, length(allfiles)*0.01)

allfilesSample <- str_replace_all(allfilesSample,"[^a-zA-Z]", " ")
allfilesSample <- str_replace_all(allfilesSample," s ", "'s ")
allfilesSample <- str_replace_all(allfilesSample," t ", "'t ")
allfilesSample <- str_replace_all(allfilesSample," u ", " you ")

```


```{r}
#twitterSample <- sample(twitterWords, length(twitterWords)*0.01)
#blogsSample <- sample(blogsWords, length(blogsWords)*0.01)
#newsSample <- sample(newsWords, length(newsWords)*0.01)

```

```{r}
aFCorpus <- corpus(allfilesSample)

toks <- tokens(allfilesSample, remove_punct = TRUE)
toks2gram <- tokens_ngrams(toks, n = 2)
toks3gram <- tokens_ngrams(toks, n = 3)

unigrams <- dfm(toks, remove = stopwords("english"), tolower = TRUE)
bigrams <- dfm(toks2gram, remove = stopwords("english"), tolower = TRUE)
trigrams <- dfm(toks3gram, remove = stopwords("english"), tolower = TRUE)
```

```{r}
head(unigrams)
head(bigrams)
head(trigrams)
tempFrequencyMatrix <- textstat_frequency(unigrams, n = 20)

g <- ggplot(tempFrequencyMatrix, aes(x = reorder(feature, frequency), y = frequency))
        g <- g + labs(title = paste(deparse(substitute(n)), "top", 
                        deparse(substitute(frequencyMatrix)), sep = " "),
                        x = "N-Gram", y = "Frequency")
        g + geom_bar(stat="identity", fill="black", colour="black") + coord_flip()  
        
tempFrequencyMatrixBigrams <- textstat_frequency(bigrams, n = 20)

g <- ggplot(tempFrequencyMatrixBigrams, aes(x = reorder(feature, frequency), y = frequency))
        g <- g + labs(title = paste(deparse(substitute(n)), "top", 
                        deparse(substitute(frequencyMatrix)), sep = " "),
                        x = "N-Gram", y = "Frequency")
        g + geom_bar(stat="identity", fill="blue", colour="black") + coord_flip()       
        
tempFrequencyMatrixTrigram <- textstat_frequency(trigrams, n = 20)

g <- ggplot(tempFrequencyMatrixTrigram, aes(x = reorder(feature, frequency), y = frequency))
        g <- g + labs(title = paste(deparse(substitute(n)), "top", 
                        deparse(substitute(frequencyMatrix)), sep = " "),
                        x = "N-Gram", y = "Frequency")
        g + geom_bar(stat="identity", fill="red", colour="red") + coord_flip()           
```



## 4. Get feedback on your plans for creating a prediction algorithm and Shiny app. ##

There is some uncertainty in the plans. Mostly, I plan to continue examine n Grams
of order 1-2-3-4 and predicting the results based on a simple fall-back strategy.

Try to find 4-grams and then move to lower numbers if nothing similar is found.

The most concerning part is smoothing and predicting the unknown words.
Another concern is a very limited amount of time (must be on the fly) and resources.